\documentclass[12pt]{article}
\usepackage{xcolor}
\definecolor{darkgray}{HTML}{333333}
\definecolor{lightgray}{HTML}{999999}
\usepackage{geometry}
\usepackage{enumitem}
\setlength\parindent{0pt}
\usepackage{hyperref}
\usepackage{bold-extra}
\usepackage{hanging}
\usepackage{fontawesome}
\pagestyle{plain}
\pagenumbering{gobble}
\geometry{left=0.5in, top=0.3in, right=0.5in, bottom=0.3in}
\hypersetup{
  colorlinks=true,
  linkcolor=black,
  filecolor=magenta,
  urlcolor=black,
}

\begin{document}
\noindent
\centering

\begin{LARGE}

  \textsc{\textbf{Taehoon
  (Tae) Song}}

\end{LARGE}

\vspace{1mm}

\begin{small}
  \qquad
  \href{https://taehoonsong.com}{TaehoonSong.com}\qquad\textbar\qquad\href{mailto:DataEngineer@TaehoonSong.com}{DataEngineer@TaehoonSong.com}\qquad\textbar\qquad{Washington, DC}\ \qquad
\end{small}

\raggedright

\vspace{1mm}


\hrulefill

\begin{large}
  \textsc{\textbf{Current Work Experience}}
  \vspace{-3mm}
\end{large}

\textcolor{lightgray}{\hrulefill}\\

\begin{small}
  
  \textbf{Cohen Milstein Sellers \& Toll, PLLC} \hfill \textcolor{gray}{Washington, DC}
  
  \textit{Senior Data Engineer} \hfill 
  \textcolor{gray}{Jan 2026 -- Present}
  
  
  \textit{Data Engineer} \hfill 
  \textcolor{gray}{Sep 2022 -- Dec 2025}
  
  
  \vspace{-2mm}

  \begin{itemize}[leftmargin=0.5cm]
      \setlength\itemsep{-1mm}
      
    \item Develop Python solutions that help find new case opportunities, streamline ETL processes, or provide user interfaces for various scripts; create and maintain data solutions for litigation support.
      
    \item Refactor or replace legacy Python, SQL, and VBA code to keep up with modern security and coding standards; migrate all authentication systems to use SSO.
      
    \item Design, implement, maintain, and optimize data pipelines, databases, and cloud infrastructures.
      
    \item Evaluate AI solutions for the Firm with respect to data privacy, security, and impact as a member of the Firm's AI Committee.
      
  \end{itemize}
  \vspace{-2mm}
  
\end{small}
\vspace{-2mm}



\hrulefill

\begin{large}
  \textsc{\textbf{Relevant Work Experience}}
  \vspace{-3mm}
\end{large}

\textcolor{lightgray}{\hrulefill}\\

\begin{small}
  
  \textbf{Grant Thornton LLP} \hfill \textcolor{gray}{Washington, DC}
  
  \textit{Manager -- Statistician} \hfill 
  \textcolor{gray}{Aug 2022}
  
  
  \textit{Senior Associate -- Statistician} \hfill 
  \textcolor{gray}{May 2021 -- July 2022}
  
  
  \vspace{-2mm}

  \begin{itemize}[leftmargin=0.5cm]
      \setlength\itemsep{-1mm}
      
    \item Designed efficient statistical samples for federal and state taxes, audits, and other program analytic purposes, saving hundreds to thousands of staff hours per engagement.
      
    \item Helped win over \$8 million in government contract awards in 2022 by authoring technical sections related to statistical sampling and data analytics in RFPs.
      
    \item Researched and implemented efficient sampling methodologies and automated internal processes via R and Python scripting; conducted simulation studies to estimate sampling efficiency, statistical inference and prediction performance, and confidence coverage.
      
  \end{itemize}
  \vspace{-2mm}
  
  \textbf{Cohen Milstein Sellers \& Toll, PLLC} \hfill \textcolor{gray}{Washington, DC}
  
  \textit{Data Analyst} \hfill 
  \textcolor{gray}{Jun 2016 -- May 2019}
  
  
  \vspace{-2mm}

  \begin{itemize}[leftmargin=0.5cm]
      \setlength\itemsep{-1mm}
      
    \item Researched securities frauds and market manipulation involving various financial instruments; frequently worked with Antitrust or ERISA practice group attorneys to assist with financial data analysis.
      
    \item Analyzed trading data sets, recognized trends and patterns, validated data integrity; audited and monitored investment data for institutional investors to calculate potential damages relating to securities class actions.
      
    \item Developed custom data pipelines by integrating Bloomberg API, VBA, SQL, and Python to automate and assist with efficient data analysis, formatting, and validation.
      
  \end{itemize}
  \vspace{-2mm}
  
  \textbf{RiskEcon Lab, New York University Courant Institute} \hfill \textcolor{gray}{New York, NY}
  
  \textit{Research Intern} \hfill 
  \textcolor{gray}{Oct 2015 -- May 2016}
  
  
  \vspace{-2mm}

  \begin{itemize}[leftmargin=0.5cm]
      \setlength\itemsep{-1mm}
      
    \item Aggregated and analyzed biodiversity data from proprietary and federal databases; reviewed literature on biodiversity data collection methods.
      
    \item Analyzed quantitative data from the railroad transportation industry to implement a financial model that considers potential economic and environmental losses due to derailments.
      
    \item Impacted policies and legislation at the state level by identifying challenges and problems through data-driven analysis; prepared and presented statistical reports to advocacy groups.
      
  \end{itemize}
  \vspace{-2mm}
  
\end{small}
\vspace{-2mm}



\hrulefill

\begin{large}
  \textsc{\textbf{Education}}
  \vspace{-3mm}
\end{large}

\textcolor{lightgray}{\hrulefill}\\

\begin{small}
  
  \textbf{George Mason University - Volgenau School of Engineering} \hfill
  \textcolor{gray}{Fairfax, VA}

  \textit{Master of Science -- Statistics} \hfill
  \textcolor{gray}{Gradudated May 2021}

  \vspace{1mm}
  
  \textbf{New York University - Stern School of Business} \hfill
  \textcolor{gray}{New York, NY}

  \textit{Bachelor of Science -- Accounting and Business Statistics} \hfill
  \textcolor{gray}{Gradudated May 2016}

  \vspace{1mm}
  
  \vspace{-2mm}
\end{small}



\hrulefill

\begin{large}
  \textsc{\textbf{Technical Skills}}
  \vspace{-3mm}
\end{large}

\textcolor{lightgray}{\hrulefill}\\

\begin{small}
  Python, SQL, Linux, Bash, VBA, Git, R, Nix, Azure, SAS
\end{small}



\end{document}
